WI FastPlants: Heritability of number of cotelydons

### 2020-07-31 cotyledon-data-analysis.Rmd
added mosaic

### Data visualization
```{r}
library(graphics)
mosaicplot(dt, shade = TRUE, las=2, main="Cotelydons")
```

>>>>

### Data visualization
```{r}
library(graphics)
mosaicplot(dt, shade = TRUE, las=2, main="Cotelydons")

library(ggmosaic)
ggplot(data = dat2) +
  geom_mosaic(aes(x = product(cots), fill=generation))
```
